### 2013-07-10 tests_Housing.Rmd
some more graphics

```{r}
set.seed(101)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=50)

@@

save(report, file="Housing300.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300.txt")

>>>>

```{r}
set.seed(202)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, lambda=0.975)

@@

save(report, file="Housing300_lambda0.975.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda0.975.txt")
